---
title: "loop_through_list_of_kHz"
output: html_document
date: "2023-05-01"
---

# Loading Packages
```{r}
pacman::p_load('tidyverse', 'ggplot2','viridis')
```

## Looking at specific frequency in kHz Insert folder here
```{r}
pathname <- "./Bloed_data2_2ms/"
kHz_identifier <- c("1kHz","2kHz","4kHz","6kHz","8kHz","10kHz","12kHz","14kHz","16kHz","18kHz","20kHz")
list_of_pathnames <- paste0(pathname,kHz_identifier)

List_of_files <- c()
for(pathname_from_list in list_of_pathnames) {
  # Save list of files into a temporary placeholder-list
  temp_list_of_files <- list.files(path = pathname_from_list,
                            recursive = TRUE,
                            pattern = "\\.txt$",
                            full.names = TRUE)
  
  #Append placeholder (add to the end of) final list of files
  List_of_files <- append(List_of_files, temp_list_of_files)
}
```

### Make a dataframe from list of files, edit frequency here
```{r}
super_dataframe <- List_of_files %>%
  purrr::set_names(.) %>%
  map_df(read_table, .id = "FileName", col_names = FALSE)
```

```{r}
# Lav en liste af tidspunkter
tidspunkter <- seq(0, 111, length.out = 532)

Df <- super_dataframe %>%
  pivot_wider(names_from = FileName, values_from = X1) %>% 
  unnest() %>%  
  mutate(Tid_i_ms = tidspunkter)

```

```{r}
# # Plot ERP
# Df %>% tidyr::gather("id", "value", 1:4) %>% 
#   ggplot(., aes(x = Tid_i_ms, y = value), group=variable)+
#   geom_line()
```


```{r}
# Vælger område med aktionspotentiale, ændrer her hvis punkter ikke skal tages med i tærskelvurdering
aktion_Df <- Df[30:80,1:63] # Vælger output 30:80, for alle kolloner undtagen tid

# Lav liste af aktion-differns
P2P <- apply(aktion_Df,2,max)-apply(aktion_Df,2,min)
```

## Updater kHz liste
```{r}
#kHz liste til Tarskel-df
kHz_liste <- c()
# 3-Missing observations 101dB for 14, 18 & 20 kHz
for(i in kHz_identifier[1:7]){
  for(loop_through_range in 1:6){
    kHz_liste <- append(kHz_liste, i)
  }
}
# Manually add last kHz to counter lost data_files
# for looping through 5 lowest dB
for(loop_through_range in 1:5){
    kHz_liste <- append(kHz_liste, kHz_identifier[8:8])
}
# 16 kHz is normal
for(loop_through_range in 1:6){
    kHz_liste <- append(kHz_liste, kHz_identifier[9:9])
}
# 5 lowest for 18-20 kHz
for(i in kHz_identifier[10:11]){
  for(loop_through_range in 1:5){
    kHz_liste <- append(kHz_liste, i)
  }
}
```

## Updater decibel intervaler
```{r}
#Lav liste med alle amplituder
Decibel <- seq(51, 101, length.out = 6)
#kHz liste til Tarskel-df
dB_liste <- c()
# 3-Missing observations 101dB for 14, 18 & 20 kHz
for(i in 1:7){
  for(dB_ID in Decibel[1:6]){
    dB_liste <- append(dB_liste, dB_ID)
  }
}
# Manually add last kHz to counter lost data_files
# for looping through 5 lowest dB
for(dB_ID in Decibel[1:5]){
    dB_liste <- append(dB_liste, dB_ID)
}
# 16 kHz is normal
for(dB_ID in Decibel[1:6]){
    dB_liste <- append(dB_liste, dB_ID)
}
# 5 lowest for 18-20 kHz
for(i in 1:2){
  for(dB_ID in Decibel[1:5]){
    dB_liste <- append(dB_liste, dB_ID)
  }
}
```



```{r}
# laver dataframe med Decibel og P2P
# Tarskel <- do.call(rbind.data.frame, Map('c', P2P, Decibel))
Tarskel <- data.frame(P2P,dB_liste, kHz_liste)



# Update collumn names
colnames(Tarskel)[1] <- "PtPmV"
colnames(Tarskel)[2] <- "Amplitude"
colnames(Tarskel)[3] <- 'kHz'

```

# Linear model of Amplitude given PtP mV 
## Not usefull in looping version for creating plot :)
```{r}
# m.1 <- lm(Amplitude ~ PtPmV, data = Tarskel) # Create linear regression
# summary(m.1) # Give a summary of linear regression (sanity check)
# 
# print(m.1$coefficients[1]) #Unrounded intercept for better plotting
# 
# model_intercept <-round(m.1$coefficients[1],2) # Get intercept with x-axis, rounded to 2 decimals
# text_string_for_plot <- paste("Intercept:
# ", model_intercept)

```
# Crazy filtering experiment 1.0
```{r}
filterd_Tarskel <- Tarskel %>% 
  filter(P2P > 8) %>% 
  group_by(kHz) %>% 
  slice_head(n = 3)


filterd_Tarskel %>% 
  group_by(kHz) %>% 
  count()



```

# Order factors (kHz), så de ikke rangeres alfabetisk
```{r}
filterd_Tarskel$kHz <- factor(filterd_Tarskel$kHz, levels = kHz_identifier)
filterd_Tarskel <- filterd_Tarskel %>% arrange(kHz)


```


# GIGAPLOT
```{r}
Titel <- "GIGAPLOT"
HEXCODES_COLOR <- c("#AC3983", "#AC3983", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")


filterd_Tarskel %>%
  ggplot(aes(x = Amplitude, y = PtPmV, color = kHz)) +
  
  geom_smooth(method = "lm", se = FALSE, fullrange=TRUE)+
  xlim(50,101)+ ylim(-10,60)+
  xlab("Amplitude dB")+ ylab("Peak-to-Peak mV")+ ggtitle(Titel)+
  scale_color_brewer(palette = "Paired")

  #scale_color_viridis(11)+
  #theme_minimal()
  #scale_color_discrete(HEXCODES_COLOR)
```



# plot enkelt
Df %>% tidyr::gather("id", "value", 4:4) %>% 
  ggplot(., aes(Tid_i_ms, value))+
  geom_line(size = 1, colour= "magenta")
  

  
  
(P2P)







